---
title: "Student Math Score Prediction"
output: html_notebook
---

```{r}
# Import necessary libraries
library(tidyverse)
library(moderndive)
library(skimr)
library(corrplot)
library(lmtest)
```



```{r}
df <- read.csv('StudentsPerformance.csv') 
head(df)
```
```{r}
skim(df)
```
Dataset Structure

```{r}
# Let's vie our dataset structure
str(df)
```

Check duplicated data
```{r}
duplicated_rows <- duplicated(df)

# Print the duplicated rows
print(df[duplicated_rows, ])
```
Check missing values in the dataset

```{r}
# Let's chek is ther missing values in the dataset
sum(is.na(df))
```
```{r}
# View the math score distribution
hist(df$math.score)

```

Distribution of Student Reading Score
```{r}
hist(df$reading.score)
```

Distribution of student writing score
```{r}
hist(df$writing.score)
```
Correlation between math score, reading score and writing score

```{r}
df2 <- df[, c('math.score','reading.score','writing.score')]
cordf2 <- cor(df2)
```


```{r}
corrplot(cordf2, method="circle", type='upper', tl.cex=0.8, tl.col = 'black')
```
Based on correlation plot above, the three feature has positive correlation


```{r}
plot(df$math.score, df$writing.score, main = "Relation between Math Score and Writing Score", xlab = "Math Score", ylab = "Writing score", pch = 16, col = "blue")
```
Math 



```{r}
plot(df$math.score, df$reading.score, main = "Relation between Math Score and Reading Score", xlab = "Math Score", ylab = "Reading score", pch = 16, col = "blue")
```
Based on the plot above, mathematics scores have a relationship with reading scores

```{r}
plot(df$reading.score, df$writing.score, main = "Relation between Writing Score and Reading Score", xlab = "Reading Score", ylab = "Writing score", pch = 16, col = "blue")
```
Based on the plot above, mathematics scores have a relationship with writing scores

```{r}
ggplot(df, aes(x = race.ethnicity)) +
  geom_bar(stat = "count", fill = "blue") +
  labs(title = "How Many Each of Race Ethnicity", x = "Categories", y = "Count")
```
Based on barplot above, group c was student majority race ethnicity 

```{r}
ggplot(df, aes(y = parental.level.of.education)) +
  geom_bar(stat = "count", fill = "blue") +
  labs(title = "Student Parental level of education", x = "Count", y = "Categories")
```
Based on the plot above, the most student parent level education is associate's degree and some college


```{r}
ggplot(df, aes(y = lunch)) +
  geom_bar(stat = "count", fill = "blue") +
  labs(title = "Student lunch categories", x = "Count", y = "Categories")
```

Based on the plot above, more students eat free/reduced lunch


```{r}
ggplot(df, aes(y = test.preparation.course)) +
  geom_bar(stat = "count", fill = "blue") +
  labs(title = "Student that take test preparation course", x = "Count", y = "Categories")
```
Based on the plot above, more student don't complete the preparation test course 


```{r}
pivot_table <- df %>%
  group_by(gender) %>%
  summarise(
    Avg_Math_score = mean(math.score),
    avg_reading_score = mean(reading.score),
    avg_writing_score = mean(writing.score)
  )

print(pivot_table)
```
Based on the Pivot table above, male student has higher average math score than female student. But the female students has higher average reading and writing score then male students

```{r}
pivot_table <- df %>%
  group_by(race.ethnicity) %>%
  summarise(
    Avg_Math_score = mean(math.score),
    avg_reading_score = mean(reading.score),
    avg_writing_score = mean(writing.score)
  )

print(pivot_table)
```
Based on the Pivot table above, group E have the highest average score of math, reading and writing.

```{r}
pivot_table <- df %>%
  group_by(parental.level.of.education) %>%
  summarise(
    Avg_Math_score = mean(math.score),
    avg_reading_score = mean(reading.score),
    avg_writing_score = mean(writing.score)
  )

print(pivot_table)
```
Based on the Pivot table above, student with master degree level parent education have the highest average score of math, reading and writing.


```{r}
pivot_table <- df %>%
  group_by(lunch) %>%
  summarise(
    Avg_Math_score = mean(math.score),
    avg_reading_score = mean(reading.score),
    avg_writing_score = mean(writing.score)
  )

print(pivot_table)
```
Based on the Pivot table above, student with standard lunch have higher average score than student with free/reduced lunch


```{r}
pivot_table <- df %>%
  group_by(test.preparation.course) %>%
  summarise(
    Avg_Math_score = mean(math.score),
    avg_reading_score = mean(reading.score),
    avg_writing_score = mean(writing.score)
  )

print(pivot_table)
```
Based on the Pivot table above, student that completed preparation test course have higher average score than student that not completed preparation test course

## Linear Regression 1
```{r}
reg1<- lm(math.score~ reading.score+writing.score, data=df)

```


```{r}
get_regression_table(reg1)

```


```{r}
get_regression_points(reg1)
```


```{r}
reg1_eval <- get_regression_summaries(reg1)
```


```{r}
ggplot(df, aes(x = math.score, y = c(reading.score, writing.score), color = ethnicity)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Age", y = "Teaching score", color = "Ethnicity")
```

## Linear Regression 2
```{r}
reg2<- lm(math.score~ gender+lunch+test.preparation.course+reading.score, data=df)
```

```{r}
get_regression_table(reg2)
```

```{r}
get_regression_points(reg2)
```

```{r}
reg2_eval <- get_regression_summaries(reg2)
reg2_eval
```


## Linear Regression 3
```{r}
reg3<- lm(math.score~ gender+lunch+reading.score+writing.score, data=df)
```

```{r}
get_regression_table(reg3)
```
```{r}
get_regression_points(reg3)
```


```{r}
reg3_eval <- get_regression_summaries(reg3)
reg3_eval
```
